### 2019-12-16 Statistical Methods/05_sampling-distributions.rmd
statistical methods
statistical methods

```{r, echo = T}

@@

```{r, echo = T}

```{r, echo = T}

>>>>

```{r, echo = T}
pnorm(4, mean = 5, sd = sqrt(5^2 / 25))
```

```{r, echo = T}
pnorm(7, mean = 5, sd = sqrt(5^2 / 25), lower.tail = F)
```

```{r, echo = T}
pnorm(7, mean = 5, sd = sqrt(5^2 / 25)) - pnorm(3, mean = 5, sd = sqrt(5^2 / 25))
```

### 5.10

Someone claims that within a certain neighborhood, the average cost of a house is $\mu = \$100,000$ with a standard deviation $\sigma = \$10,000$. Suppose that based on n = 16 homes, you find that the average cost of a house is $\bar{X} = \$95,000$. Assuming normality, what is the probability of getting a sample mean this low or lower if the claims about the mean and standard deviation are true?

```{r, echo = T}
pnorm(95e3, mean = 1e5, 1e4 / sqrt(16) )
```

### 5.11

In the previous problem, what is the probabiility of getting a sample mean between $97,500 and $102,500?

```{r, echo = T}
pnorm(1025e2, mean = 1e5, 1e4 / sqrt(16), lower.tail = T) - pnorm(975e2, mean = 1e5, 1e4 / sqrt(16))
```

### 5.12

A company claims that the premiums paid by its clients for auto insurance has a normal distribution with mean $\mu = \$750$ dollars and standard deviation $\sigma = 100$.

Assuming normality, what is the probability that for $n = 9$ randomly sampled clients, the sample mean will have a value between $700 and $800?

```{r, echo = T}
s <- 100 / sqrt(9)

pnorm(800, mean = 750, sd = s) - pnorm(700, mean = 750, sd = s)
```

### 5.13

Imagine you are a health professional interested in the effects of medication on the diastolic blood pressure of adult women. For a particular drug being investigated, you find that for $n = 9$ women, the sample mean is $\bar{X} = 85$ and the sample variance is $s^2 = 160.78$.

Estimate the standard error of the sample mean, assuming random sampling.

```{r, echo = T}
sqrt(160.78 / 9)
```

### 5.14

You randomly sample 16 observations from a discrete distribution with mean $\mu = 36$ and variance $\sigma^2 = 25$.

```{r, echo = T}
n <- 16; mu <- 36; variance <- 25

s <- sqrt(variance / n)

@@

Use the central limit therom to determine:

a.) $P(\bar{X} \le 34)$

```{r, echo = T}
pnorm(34, mean = mu, sd = s)
```

b.) $P(\bar{X} \le 37)$

```{r, echo = T}
pnorm(37, mean = mu, sd = s)
```

c.) $P(\bar{X} \ge 33)$

```{r, echo = T}
pnorm(33, mean = mu, sd = s, lower.tail = F)
```

d.) $P(34 \le \bar{X} \le 37)$

```{r, echo = T}
pnorm(37, mean = mu, sd = s) - pnorm(34, mean = mu, sd = s)
```

### 5.15

You sample 25 observations from a nonnormal distribution with mean $\mu = 25$ and variance $\sigma^2 = 9$.

Use the central limit therom to determine:

a.) $P(\bar{X} \le 24)$

```{r, echo = T}
```

b.) $P(\bar{X} \le 26)$

```{r, echo = T}
```

c.) $P(\bar{X} \le 24)$

```{r, echo = T}
```

d.) $P(24 \le \bar{X} \le 26)$

```{r, echo = T}
```

### 5.16

Describe a situation where reliance on the central limit theorm to determine $P(\bar{X} \le 24)$ might be unsatisfactory.

### 5.17

Describe situations where a normal distribution provides a good approximation of the sampling distribution of the mean.

### 5.18

For the values 4, 8, 23, 43, 12, 11, 32, 15, 6, 29, verify that the McKean-Schrader estimate of the standard error of the mean is 7.57.

### 5.19

In the previous exercise, how would you argue that the method used to estimate the standard error of the median is a reasonable approach?

### 5.20

For the values 5, 7, 2, 3, 4, 5, 2, 6, 7, 3, 4, 6, 1, 7, 4, verify that the McKean-Schrader estimate of the standard error of the median is 0.97.

### 5.21

In the previous excersize, how would you argue that the method used to estimate the standard error of th median might be highly inaccurate?

### 5.22

In Exercise 20, would it be advisable to approximate $P(M \le 4)$, the probability that the sample median is less than or equal to 4, using Equation (5.7)?

### 5.23

For the values, 2, 3, 5, 6, 8, 12, 14, 18, 19, 22, 201, why would you suspect that the McKean-Schrader estiamte of the standard error of the median will be smaller than the standard error of the mean?
